---
title: "Math 265: Homework 3"
subtitle: "Exploratory Data Analysis"
author: "Your Name"
date: "Due Sunday, February 18, 2024"
format: 
    gfm: 
      toc: true
      toc-depth: 2
      fig-height: 4
      fig-width: 9
editor: visual
execute: 
  echo: true
  warning: false
  eval: false
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(ggthemes)
```

# Introduction

Use this document as a template for writing up your assignment. You should delete this line before submitting. Remove the `eval=FALSE` option on line 16 so that your chunks will be executed when you knit this file.

# Movie Data Analysis

In this analysis, you will investigate IMDB and Rotten Tomatoes ratings for a random sample of 651 movies. The following command loads the data into a dataframe named `movies.`.[^1]

[^1]: This problem adapts a tutorial prepared by Iain Carmichael and makes use of the [movies data](http://www2.stat.duke.edu/~mc301/data/movies.html) generously provided by Mine Cetinkaya-Rundel.

```{r}
# load the data from an R binary data file into the data frame movies 
load(file = "data/movies.Rdata")
```

## Data Overview

a.  Use the R command that will give an overview of the `movies` data frame by showing all the variable names and the first few observations from each.

**Answer:**

```{r}

```

## Exploratory Data Analysis

b.  Use `count()` to obtain frequency tables for four factor variables: `title_type`, `genre` and `critics_rating` and `audience_rating`.

**Answer:**

```{r}

```

c.  Make a histogram of **imdb_rating**.

**Answer:**

```{r}

```

d.  Repeat the previous histogram but this time set bins such that the bars have width 1 and are centered at whole number values of `imdb_rating` (1, 2, 3, ...).

**Answer:**

```{r}

```

e.  Write two or three sentences summarizing your observations about the `imdb_rating` scores.

**Answer:**

f.  Create a scatterplot with the Rotten Tomatoes `critic_score` (y) and corresponding imdb ratings (x). Add a smoothing line (no standard error band). If necessary, add jittering to avoid overplotting.

**Answer:**

```{r}

```

g.  Now try some alternatives to traditional scatterplots for exploring the relationship between these two variables. In practice, some of these would be more appropriate for larger data sets but show that you can construct them for this pair of variables. Create each of the following plots described in the text of this section: (i) `geom_bin2d()`; (ii) `geom_hex()`; and (iii) a boxplot using either `cut_width()` or `cut_number()` that has ten boxes and whose width is proportional to the number of movies represented.

**Answer:**

```{r}

```

h.  Inspect your scatterplots from part (f) and (g) and write a couple sentences observing the nature, strength and direction of the covariation of these two variables.

**Answer:**

```{r}

```

h.  Use faceting to consider whether the relationship between Rotten Tomatoes rating and IMDB rating depends on the MPAA ratings. For each facet, add a least squares regression line without a standard error bar and write a couple sentences with your observations.

**Answer:**

```{r}

```

i.  Instead of faceting, create a graph that shows how the relationship between IMDB rating and Rotten Tomatoes rating is related to `runtime`. That is, add `runtime` as a third variable to your scatterplot from (f) and map it to an aesthetic. You may find it useful to make use of one of the `cut_` functions for incorporating `runtime`. Comment on what you see.

**Answer:**

```{r}

```

## Wrangling the Movie Data

(j) Use `select()` to create a new data set **movies2** containing just the following variables: `title`, `runtime`, `genre`, `mpaa_rating`, `thtr_rel_year`, `imdb_rating`, `imdb_num_votes`, `critics_score`, `audience_score`, and `best_pic_win`.

**Answer:**

```{r}

```

(k) Compute the means of all the numeric variables. Note which variables have NA values for their means.

**Answer:**

```{r}

```

(l) You should have found that the `runtime` variable is missing for at least one movie. Identify the movie(s) missing `runtime` data and track down (Google) the missing data. Replace the NA value(s) with their correct value(s) and re-compute the mean for `runtime`.

**Answer:**

```{r}

```

(m) Compute the mean `runtime` for each `genre` and then create a bar chart of the mean `runtime` by `genre`. Which genres have the lowest and highest average `runtime`?

**Answer:**

```{r}

```
